---
output:
  github_document:
    toc: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# Full Resolution O Rly Book Covers
Full resolution images of the O RLY book covers made by [The Practical Dev](http://twitter.com/thepracticaldev)

These are parody images and are not associated with the actual [O'Reilly Media](http://www.oreilly.com/) company or brand.

Here is the [O RLY Cover Generator](http://dev.to/rly).

These images can be used for non-commercial purposes under the [Attribution-NonCommercial 2.0 Generic](https://creativecommons.org/licenses/by-nc/2.0/)

# Gallery of the O Rly Book Covers

Clickable gallery, which is created from a small chunk of R code in an executable R Markdown [`README.Rmd`](README.Rmd). [This gist](https://gist.github.com/jennybc/0239f65633e09df7e5f4) shows similar syntax but with markdown image links, instead of html.

```{r make-smaller-pngs, include = FALSE}
library(magick)
library(purrr)
fig_files <- list.files(pattern = "-big.png$")
fig_files_smaller <- gsub("(^.*)(\\.png$)", "\\1-smaller\\2", fig_files)

## make sure all PNGs exist in a 'smaller' version
fig_files_needed <- !file.exists(fig_files_smaller)
if (any(fig_files_needed)) {
  figs <- map(fig_files[fig_files_needed], image_read)
  figs %>% 
    map(image_scale, geometry = "400") %>% 
    map2(fig_files_smaller[fig_files_needed], image_write)
}
fig_files_smaller <- gsub("(^.*)(\\.png$)", "\\1-smaller\\2", fig_files)  
```

```{r make-gallery, results = "asis", echo = FALSE}
## the real business is here
tags <- sprintf("<a href=\"%s\"><img src=\"%s\"></a>",
                fig_files, fig_files_smaller)
cat(tags)
```
